\subsection{Nuu-chah-nulth}

\subsubsection{Area 23}

There was mixed success with spawn on boughs (SOB) harvests in 2024
but overall, SOB harvest success was improved compared to the past few years.
Spawn was distributed fairly broadly from Mayne Bay, St. Ines, Forbes Island,
and Salmon Beach to Macoha and the entrance of Ucluelet Harbour
around Spring Cove and Stuart Bay.
For the most part, spawning duration in all areas was short
except for St. Ines Island where spawning occurred over two days.
As in the past several years, the short duration of most spawns
necessitated harvesters be on-site at the time of spawning
to get boughs in the spawn.
There was very limited success for SOB in all areas
except Spring Cove and Stuart Bay.
Great success for spawn in Spring Cove and Stuart Bay
with branches with covered with 6-8 layers. 

\subsubsection{Area 24}

As in 2023, spawning activity in Area 24 began in
early January in Hesquiaht Harbour and spread to several other areas
throughout Clayoquot Sound in through February and March.
The Nations were pleased to see spawn in new areas such as
Epper Passage and Stubbs Island.
Both Hesquiaht and Ahousaht had very successful SOB harvests
from their territories at Bawden Bay, Matilda Inlet and Anton Spit,
with boughs having up to 25 layers.
Spawn was also observed in Tla-o-qui-aht Territories such as Stubbs Island,
but they held off setting boughs as herring spawning
had not been regularly observed in this area for many years and
Tla-o-qui-aht did not want to disturb them.  

\subsubsection{Area 25}

All Nations had some success with SOB harvests.
Ehattesaht set trees in Port Langford with mixed success.
Only 40\% of the boughs had sufficient layers (3-4) to harvest.
Ehattesaht also harvested about 40 pounds of kelp and eel grass
from spawn events at Double Island, the back side of Harbour Island
and in Mary Basin.
Nuchatlaht set trees in Rosa Harbour and Port Langford and
in Nuchatlitz Bay with only a few boughs having 1-2 layers
resulting in a minimal harvest.
Nuchatlaht also harvested about 120 pounds of kelp and eel grass from
the spawn events at Double Island, the back side of Harbour Island, and
in Mary Basin.
MMFN set all their trees in Yuquot (Friendly Cove)
with all boughs having 8-9 layers of eggs and
commenting that is was the best spawn in over five years.
